Universal Anonymous Signatures

### 2022-10-04 prism-backend/research/gsac/app-related-proofs.tex
30 pages.

We prove that our \CUASGS construction is a secure group signature scheme,
according to \cite{bsz05}, if the underlying \CUASGen construction is secure.

@@

We prove that our \CUASRing construction is anonymous and unforgeable, if
the underlying $\CUASGen^{hide-iss}$ construction is secure.

>>>>

We prove that our \CUASGS construction is an anonymous, traceable, and
non-frameable group signature scheme, according to the model in \cite{bsz05}, if
the underlying \CUASGen construction is secure.

@@

We prove that our \CUASRing construction is anonymous and unforgeable, in the
model given in \cite{bkm06}, if the underlying $\CUASGen^{hide-iss}$
construction is secure.

### 2022-10-04 prism-backend/research/gsac/app-uas-proofs.tex
30 pages.

Next, we define the \SimSetup, \ExtractIssue, \ExtractSign functions. \SimSetup
(formally defined in \figref{fig:helper-funcs}) essentially replaces the
\Setup algorithm of each NIZK with the corresponding \NIZKSimSetup algorithm,
and returns the generated parameters along with the
trapdoors. \ExtractIssue and \ExtractSign simply run the \Extract functions
of the corresponding \NIZK scheme, leveraging the trapdoor produced during
\SimSetup. Note that, in our games definitions, both algorithms are always run
over signatures that have already been verified (in the case of \ExtractSign)
or transcripts maintained by honest issuers (in the case of \ExtractIssue).
Thus, the zero-knowledge proofs they contain are valid. Concerning \SimSetup,
due to the zero-knowledge and simulation extractability properties
(respectively) of the underlying NIZKs, its result is indistinguishable from
that of \Setup, and the extracted values match those used as witnesses in the
proofs.

@@

\begin{proof}[\thmref{thm:issue-forge-uas}; Issuance unforgeability of \CUASGen]
  We show that the probability that \fissue outputs a wrong $\yissue$ value is
  negligible, as well as the probability that the issued credential, and any
  supporting credential used in the request, do not all belong to a same known
  (honest or corrupt) user.

@@

  Finally, the adversary wins if the \uid associated to the {\cid}s involved in
  the request (i.e., both the \cid output by the adversary, as well as those
  used to support its issuance) is not in \HU or \CU. This can happen if: (1)
  all {\cid}s have the same owner \uid, but this \uid is different to all known
  {\uid}s; or (2) $\OWNR[\scid] = \bot$ which, by definition of \OWNR happens if
  not all of the involved {\cid}s in \scid have the same owner. Since the NIZK
  used for $\NIZKRel_{\Issue}$ is simulation extractable -- where the issuer
  verifies that all credentials are bound to the same \usk -- and due to
  correctness of \SBCM, the probability that (2) happens is negligible, which
  means that all involved {\cid}s have the same owner. Also, regarding (1), this
  owner must be in either \HU or \CU as the \cid output by the adversary in step
  2 has been produced via \ISSUE or \OBTISS which, by definition, only accept
  known {\uid}s. Thus, the probability that \adv~wins the \ExpForgeIssue game is
  negligible.
  \qed
\end{proof}

\subsection{Signature Unforgeability}

>>>>

Next, we define the \SimSetup, \ExtractIssue, \ExtractSign, and \VerCred
functions. \SimSetup (formally defined in \figref{fig:helper-funcs}) essentially
replaces the \Setup algorithm of each NIZK with the corresponding \NIZKSimSetup
algorithm, and returns the generated parameters along with the
trapdoors. \ExtractIssue and \ExtractSign simply run the \Extract functions
of the corresponding \NIZK scheme, leveraging the trapdoor produced during
\SimSetup. Note that, in our games definitions, both algorithms are always run
over signatures that have already been verified (in the case of \ExtractSign)
or transcripts maintained by honest issuers (in the case of \ExtractIssue).
Thus, the zero-knowledge proofs they contain are valid. Concerning \SimSetup,
due to the zero-knowledge and simulation extractability properties
(respectively) of the underlying NIZKs, its result is indistinguishable from
that of \Setup, and the extracted values match those used as witnesses in the
proofs. Finally, \VerCred simply calls the \SBCMVerify function with the
received data -- where \usk is signed in committed form, \cid and \attrs in
plain form, and \cred is their alleged signature by the owner of public key
\ipk.

@@

\begin{proof}[\thmref{thm:issue-forge-uas}; Issuance unforgeability of \CUASGen]
  We show that, assuming simulation extractability of the NIZK for \RelIss, and
  correctness and unforgeability of \SBCM, then \CUASGen has issuance
  unforgeability.

  Observe that we restrict to credentials issued by honest issuers. Thus, if a
  credential with identifier \cid was issued by an honest issuer, a matching
  $\trans[\cid]$ entry corresponding to its issuance must exist.
  %
  Then, $\trans[\cid] = (\yissue,\utrans)$, and \utrans contains a NIZK proof
  \proofiss proving knowledge by the (potentially corrupt) user of a witness in
  \RelIss. Since the issuer is honest, it verifies the NIZK as part of the
  issuance protocol, rejecting if the proof is not valid. Thus, by simulation
  extractability, \ExtractIssue produces a $(\upk,\usk,\lbrace (\cid_i,\attrs_i,
  \cred_i,\ipk_i) \rbrace_{i\in[n]},(\cid,\attrs,\cred,\ipk))$ tuple.

  Since credential \cid was honestly issued, simulation extractability and
  correctness of \SBCM ensure that \VerCred returns $1$ when run over the values
  output by \adv, along with the \usk extracted by \ExtractIssue. Also, by
  simulation extractability, the value output by \fissue, when evaluated upon
  the extracted values, must match the \yissue value stored alongside
  $\trans[\cid]$.
  %
  In addition, the adversary wins if the \uid associated to the {\cid}s involved
  in the request (i.e., both the \cid output by the adversary, as well as those
  used to support its issuance) is not in \HU or \CU. This can happen if: (1)
  all {\cid}s have the same owner \uid, but this \uid is different to all known
  {\uid}s; or (2) $\OWNR[\scid] = \bot$ which, by definition of \OWNR happens if
  not all of the involved {\cid}s in \scid have the same owner. Since the NIZK
  used for \RelIss is simulation extractable -- where the issuer verifies that
  all credentials are bound to the same \usk -- and due to correctness of \SBCM,
  the probability that (2) happens is negligible, which means that all involved
  {\cid}s have the same owner. Also, regarding (1), this owner must be in either
  \HU or \CU as the \cid output by the adversary in step 2 has been produced via
  \ISSUE or \OBTISS which, by definition, only accept known {\uid}s. Thus, the
  probability that \adv~wins the \ExpForgeIssue game is negligible.

  Finally, the adversary may also win if any of the $\cred_i$ credentials (1) is
  not a valid signature by its issuer, or (2) if it is a valid signature by some
  honest issuer who did not produce it. As before, (1) has negligible
  probability due to simulation extractability of the NIZK for \RelIss. For (2),
  assume that such a $\cred_i$ exists, then, it is an \SBCM forgery -- i.e., a
  valid signature, verifiable under $\ipk_i$ belonging to an honest issuer, who
  did not produce it via a call to \OBTISS or \ISSUE. Thus, it breaks the
  one-more unforgeability property of \SBCM. By security of \SBCM, the
  probability that it happens must be negligible.
\end{proof}

\iffalse
\begin{proof}[\thmref{thm:issue-forge-uas}; Issuance unforgeability of \CUASGen]
  We show that the probability that \fissue outputs a wrong $\yissue$ value is
  negligible, as well as the probability that the issued credential, and any
  supporting credential used in the request, do not all belong to a same known
  (honest or corrupt) user.

@@

  Finally, the adversary wins if the \uid associated to the {\cid}s involved in
  the request (i.e., both the \cid output by the adversary, as well as those
  used to support its issuance) is not in \HU or \CU. This can happen if: (1)
  all {\cid}s have the same owner \uid, but this \uid is different to all known
  {\uid}s; or (2) $\OWNR[\scid] = \bot$ which, by definition of \OWNR happens if
  not all of the involved {\cid}s in \scid have the same owner. Since the NIZK
  used for $\NIZKRel_{\Issue}$ is simulation extractable -- where the issuer
  verifies that all credentials are bound to the same \usk -- and due to
  correctness of \SBCM, the probability that (2) happens is negligible, which
  means that all involved {\cid}s have the same owner. Also, regarding (1), this
  owner must be in either \HU or \CU as the \cid output by the adversary in step
  2 has been produced via \ISSUE or \OBTISS which, by definition, only accept
  known {\uid}s. Thus, the probability that \adv~wins the \ExpForgeIssue game is
  negligible.
  \qed
\end{proof}
\fi
\subsection{Signature Unforgeability}

### 2022-10-04 prism-backend/research/gsac/conclusion-paper.tex
30 pages.

The flexibility of our model is achieved via functional placeholders that
modulate the behaviour at credential issuance time, the utility
information ``leaked'' along with the produced signatures, and the utility
information extractable from already produced signatures. These functions are
computed by the users themselves, who need to prove correct computation.
Our setting combines features of anonymous credential schemes, like
attribute-based credentials and multiple issuers, which we extend with openers
(like in group signatures), but also enabling that multiple openers coexist.
This further increases the flexibility, by removing the tight issuer-opener
coupling in previous works.

For future work, an obvious line is to come up with (and implement) concrete
instantiations of our generic construction in order to evaluate efficiency in
real-world use cases. Also, it may be interesting to come up with alternative
generic constructions -- for instance, based on structure-preserving signatures.
%
Finally, in this work we focus only on utility over \emph{one} signature. But
extending our model and constructions to span utility over \emph{multiple}
signatures promises to be interesting, both regarding its modelling, the
potential use cases, and the generalization capabilities.

>>>>

Flexibility in our model is achieved via functional placeholders that
modulate the behaviour at credential issuance time, the utility
information revealed along with the produced signatures, and the utility
information extractable from already produced signatures. These functions are
computed by the users, who prove correct computation. We include features of
anonymous credential schemes, like attributes and multiple
issuers, which we extend with openers (like in group signatures), enabling
multiple openers to coexist. This further increases flexibility, by removing
the tight issuer-opener coupling in previous works.

For future work, an obvious line is to come up with (and implement) concrete
instantiations of our generic construction in order to evaluate efficiency in
real-world use cases. Alternative generic constructions are also of interest --
for instance, based on structure-preserving signatures.
%
Finally, in this work we focus only on utility over \emph{one} signature. But
extending our model and constructions to span utility over \emph{multiple}
signatures promises to be interesting, both regarding its modelling, the
potential use cases, and the generalization capabilities.
